---
title: 
author: 
date:
output:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(lme4)
library(crqa)
library(tseriesChaos)
library(SparseM)
library(dplyr)
library(caret)
library(modelr)
library(stringr)
library(data.table)
library(groupdata2)
library(Metrics)


setwd("~/Dropbox/Aarhus Universitet/Eye tracking")

#Exercise 3
Samples=read.csv('SamplesV2.csv')
Saccades=read.csv('SaccadesV2.csv')
Fixations=read.csv('FixationsV2.csv')

#Exercise
#Samples=read.csv('SamplesV3.csv')
#Saccades=read.csv('SaccadesV3.csv')
#Fixations=read.csv('FixationsV3.csv')





hist=ggplot(Fixations(aes(Duration)))+geom_histogram()

#hist=ggplot(data=Fixations,aes(Duration)+geom_histogram())










#lmer(PeakVelocity ~ SearchType + (1|ParticipantID), data = Saccades)
#summary(model1)

#lmer(? ~ SearchType + SearchOrder + (1+SearchType|ParticipantID) + (1+SearchType|SearchType))
#summary(model2)



model1=glmer(Duration ~ SearchType + Trial + (1+SearchType+Trial|ParticipantID), data=Fixations, family=gaussian(link = log))
summary(model1)

model2=glmer(Duration ~ SearchType * Trial + (1+SearchType*Trial|ParticipantID), data=Fixations, family=gaussian(link = log))
summary(model2)

model3=glmer(Duration ~ SearchType + (1+SearchType|ParticipantID), data=Fixations, Family=gaussian(link = log))
summary(model3)


#Cross validation
visualsearch=subset(Fixations, Task=="VisualSearch")

visualsearch$ParticipantID=as.character(visualsearch$ParticipantID)
visualsearch$ParticipantID=as.factor(visualsearch$ParticipantID)
visualsearch$ParticipantID=as.numeric(visualsearch$ParticipantID)

folds = createFolds(unique(visualsearch$ParticipantID),k=3)


#Simple model
n=1
error.train.simple=NULL
error.test.simple=NULL
for (i in folds)
  {
  testD=visualsearch[visualsearch$ParticipantID %in% i,]
  trainD=visualsearch[!(visualsearch$ParticipantID %in% i),]
  Mtrain = glmer(Duration ~ SearchType + (1+SearchType|ParticipantID), data=Fixations, Family=gaussian(link = log))
  pred = predict(Mtrain,testD, allow.new.levels=TRUE)
  error.train.simple[n]=Metrics::rmse(predict(Mtrain), trainD$Duration)
  error.test.simple[n]=Metrics::rmse(predict(Mtrain), testD$Duration)

  n=n+1
  
}

mean(error.train.simple)
mean(error.test.simple)




#Fixed effect model
n=1
error.train.fixed=NULL
error.test.fixed=NULL
for (i in folds)
  {
  testD=visualsearch[visualsearch$ParticipantID %in% i,]
  trainD=visualsearch[!(visualsearch$ParticipantID %in% i),]
  Mtrain = glmer(Duration ~ SearchType + Trial + (1+SearchType+Trial|ParticipantID), data=Fixations, family=gaussian(link = log))
  pred = predict(Mtrain,testD, allow.new.levels=TRUE)
  error.train.fixed[n]=Metrics::rmse(predict(Mtrain), trainD$Duration)
  error.test.fixed[n]=Metrics::rmse(predict(Mtrain), testD$Duration)

  n=n+1
  
}

mean(error.train.fixed)
mean(error.test.fixed)




#Interaction model
n=1
error.train.interaction=NULL
error.test.interaction=NULL
for (i in folds)
  {
  testD=visualsearch[visualsearch$ParticipantID %in% i,]
  trainD=visualsearch[!(visualsearch$ParticipantID %in% i),]
  Mtrain = glmer(Duration ~ SearchType * Trial + (1+SearchType*Trial|ParticipantID), data=trainD, family=gaussian(link = log))
  pred = predict(Mtrain,testD, allow.new.levels=TRUE)
  error.train.interaction[n]=Metrics::rmse(predict(Mtrain), trainD$Duration)
  error.test.interaction[n]=Metrics::rmse(predict(Mtrain), testD$Duration)

  n=n+1
  
}

mean(error.train.interaction)
mean(error.test.interaction)

```

#Noter til cross validation
Ludvigs pakke: groupdata2.
participantID passer ikke sammen, giver NAs

as.character
as.factor
as.numeric


lmer(? ~ SearchType * SearchOrder * Fixation * Trial + (1+SearchType*Fixation*Trial|ParticipantID), data=)
summary(model4)

data = x, family=gaussian(link = log)

anna: 4.2

```{r}

#Visualisation of the data

library(jpeg)
library(grid)



#example
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))
img <- readJPEG('eyetrackingscripts/foraging/ng090ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

#density
ggplot(subset(Fixations, Task=='VisualSearch' & ParticipantID=='6_3_m2' & Trial==6), aes(x = PositionX, y = PositionY)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
  scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")

```


```{r}
#Heatmap
#SEARCH
img <- readJPEG('eyetrackingscripts/foraging/ng021ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

#density
ggplot(subset(Fixations, Task=='VisualSearch' & ParticipantID=='3_1_f1' & Trial==1), aes(x = PositionX, y = PositionY)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
  scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")
```


```{r}
#Heatmap
#COUNT
img <- readJPEG('eyetrackingscripts/foraging/ng120ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

#density
ggplot(subset(Fixations, Task=='VisualSearch' & ParticipantID=='3_1_f1' & Trial==7), aes(x = PositionX, y = PositionY)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
  scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")
```

```{r}
#SCANPATHS
#Search
img <- readJPEG('eyetrackingscripts/foraging/ng021ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

ggplot(subset(Fixations, Task == 'VisualSearch' & ParticipantID=='1_1_f1' & Trial==1), aes(x=PositionX, y=PositionY, label=Fixation)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080)+
  geom_point(size = 5, alpha = 0.5) +
  geom_path(size = 1, alpha = 0.3) +
  geom_text(aes(label = Fixation, size = 5))
  

```

```{r}
#SCANPATHS
#Count
img <- readJPEG('eyetrackingscripts/foraging/ng073ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

ggplot(subset(Fixations, Task == 'VisualSearch' & ParticipantID=='2_2_f2' & Trial==5), aes(x=PositionX, y=PositionY, label=Fixation)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080)+
  geom_point(size = 5, alpha = 0.5) +
  geom_path(size = 1, alpha = 0.3) +
  geom_text(aes(label = Fixation, size = 5))
```
```{r}
#SCANPATHS
#Count
#fixed with y=1081-PositionY (inversion)

img <- readJPEG('eyetrackingscripts/foraging/ng120ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

ggplot(subset(Fixations, Task == 'VisualSearch' & ParticipantID=='3_1_f1' & Trial==7), aes(x=PositionX, y=1081-PositionY, label=Fixation)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080)+
  geom_point(size = Fixations$Duration/100, alpha = 0.5) +
  geom_path(size = 1, alpha = 0.3) +
  geom_text(aes(label = Fixation, size = 5))
```

```{r}
socialengagement=subset(Samples, Task=="SocialEngagement")

ggplot(data=socialengagement, aes(x=TrialTime, y=PupilSize,colour=Ostension))+
  geom_smooth()


ggplot(data=socialengagement, aes(x=TrialTime, y=PupilSize,colour=Directionality))+
  geom_smooth()
```
#graphs

x=TrialTime
y=PupilSize
df=Samples

g1=PartGender
g2=ActorGender

g1=Directedness
g2=Ostensiveness

geom_smooth()
facet_grid()


```{r}
img <- readJPEG('eyetrackingscripts/foraging/ng120ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

ggplot(subset(Fixations, Task == 'VisualSearch' & ParticipantID=='3_1_f1' & Trial==7), aes(x=PositionX, y=PositionY, label=Fixation)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080)+
  geom_point(size = 5, alpha = 0.5) +
  geom_path(size = 1, alpha = 0.3) +
  geom_text(aes(label = Fixation, size = 5))



#SCANPATHS
#Count
img <- readJPEG('eyetrackingscripts/foraging/ng120ws.jpg')
g <- rasterGrob(img, interpolate=TRUE)

ggplot(subset(Fixations, Task == 'VisualSearch' & ParticipantID=='3_1_f1' & Trial==7), aes(x=PositionX, y=PositionY, label=Fixation)) +
  xlim(0,1920) +
  ylim(0, 1080) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080)+
  geom_point(size = 5, alpha = 0.5) +
  geom_path(size = 1, alpha = 0.3) +
  geom_text(aes(label = Fixation, size = 5))
```




